Post MCMCglmm analyses

### 2021-04-12 Analysis/06-post_mcmcglmm_analyses.Rmd
Update 06-post_mcmcglmm_analyses.Rmd

>>>>

For the tip wise approach, the method is pretty straightforward from what I've done previously: we just measure the projection/rejection (elaboration/exploration) on each for each axis that we've drawn above. We thus end up with 100 projection/rejection score for each element (tip) in the tree for:

 * Each element against the phylo axes
 * Each element against their clade axes

```{r}
library(dispRity)
## Wrapping function
lapply.projections <- function(one_axis, trait_space) {
    return(list(
        projection = projections(as.matrix(trait_space), point1 = one_axis[1,], point2 = one_axis[2,]),
        rejection  = projections(as.matrix(trait_space), point1 = one_axis[1,], point2 = one_axis[2,], measure = "distance")))
}
## Plot rejection/projection profiles
plot.proj.rej <- function(point_list, cols, data, main) {
    ## Colour vector
    colour_vector <- cols[morphdat$clade]
    colour_vector <- adjustcolor(colour_vector, alpha.f = 1/10)
    ## lims
    lim <- range(unlist(point_list))
    plot(NULL, xlim = lim, ylim = lim, xlab = "projection", ylab = "rejection", main = main)
    ## Add each points
    plot.points <- function(one_set, colour_vector) {
        points_args <- list()
        points_args$pch <- 19
        points_args$col <- colour_vector
        points_args$x <- one_set$projection
        points_args$y <- one_set$rejection
        do.call(points, points_args)
    }

    lapply(point_list, plot.points, colour_vector)
    return(invisible())
}

## Getting the results
phylo_results_uncentered <- lapply(uncentered_major_axes$phylogeny, lapply.projections, trait_space = morphdat[, c(1,2,3)])

## Plot results
plot.proj.rej(phylo_results_uncentered, cols = colour_vector, data = morphdat, main = "Phylo elaboration/rejection")
```

But maybe it's easier to boxplot that to get the info by clade

```{r}
boxplot.proj.rej <- function(point_list, data, cols) {
    ## Get the classifier
    classifier <- data$clade    
    sort.clade.rej <- function(data, classifier) {
        return(cbind(data$rejection, classifier))
    }
    sort.clade.proj <- function(data, classifier) {
        return(cbind(data$projection, classifier))
    }
    ## Sort the data per clade
    rejections <- do.call(rbind, lapply(point_list, sort.clade.rej, classifier))
    projections <- do.call(rbind, lapply(point_list, sort.clade.proj, classifier))
    colnames(rejections)[1] <- colnames(projections)[1] <- "points"
    par(mfrow = c(2,1))
    boxplot(points ~ classifier, data = projections, col = cols, main = "Projections")
    boxplot(points ~ classifier, data = rejections, rejections, col = cols, main = "Rejections")
}

boxplot.proj.rej(phylo_results_uncentered, cols = colour_vector, data = morphdat)
```
